---
title: "SL_lab_nonlinear"
author: "David Tsai"
date: "3/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Nonlinear Models
```{r}
require(ISLR)
attach(Wage)
```


Polynomials
---------------

Use Polynomials and focus on a single predictor: age.

```{r}
fit = lm(wage ~ poly(age, 4), data = Wage)
summary(fit)
```

Make a plot of the fitted function, along with the standard errors of the fit.

```{r fig.width = 7, fig.height = 6}
agelims = range(age)
age.grid = seq(from = agelims[1], to = agelims[2])
preds = predict(fit, newdata = list(age = age.grid), se = TRUE)
se.bands = cbind(preds$fit + 2 * preds$se, preds$fit - 2 * preds$se)
plot(age, wage, col = "darkgrey")
lines(age.grid, preds$fit, lwd = 2, col = "blue")
matlines(age.grid, se.bands, col = "blue", lty = 2)
```

Other ways to do this.

```{r}
fita = lm(wage ~ age + I(age^2) + I(age^3) + I(age^4), data = Wage)
summary(fita)

plot(fitted(fit), fitted(fita))
```

Use 'anova()'

```{r}
# nested sequence of models
fita = lm(wage ~ education, data = Wage)
fitb = lm(wage ~ education + age, data = Wage)
fitc = lm(wage ~ education + poly(age, 2), data = Wage)
fitd = lm(wage ~ education + poly(age, 3), data = Wage)

anova(fita, fitb, fitc, fitd)
```


### Polynomial Logistic Regression
Fit a logistic regression model to a binary response variable, constructed from "wage".
Code the big earners ('> 250K') as 1, else 0.

```{r}
fit.bi = glm(I(wage > 250) ~ poly(age, 3), data = Wage, 
          family = binomial)

summary(fit.bi)

preds = predict(fit.bi, list(age = age.grid), se = TRUE)
se.bands = preds$fit + cbind(fit = 0, lower = -2 * preds$se, upper = 2 * preds$se)
se.bands[1:5,]
```

Apply the inverse logit mapping
$$p=\frac{e^\eta}{1+e^\eta}.$$

```{r}
prob.bands = exp(se.bands) / (1+ exp(se.bands))
matplot(age.grid, prob.bands, col = "blue", 
        lwd = c(2, 1, 1), lty = c(1, 2, 2), type = "l", ylim = c(0,.1))

points(jitter(age), I(wage > 250)/10, pch = "I", cex = .5)
```


## Splines
```{r}
require(splines)
fit = lm(wage ~ bs(age, knot = c(25, 40, 60)), data = Wage)
plot(age, wage, col = "darkgrey")
lines(age.grid, predict(fit, list(age = age.grid)), 
      col = "darkgreen", lwd = 2)
abline(v = c(25, 40, 60), lty = 2, col = "darkgreen")

# smoothing splines
fit = smooth.spline(age, wage, df = 16) # 16 degrees of freedom
lines(fit, col = "red", lwd = 2)


#leave-one-out cross validation to select the smoothing parameter
fit = smooth.spline(age, wage, cv = TRUE)
lines(fit, col = "purple", lwd = 2)
fit
```

